% !TEX encoding = UTF-8 Unicode
%----------------------------------------------------------------------------------------------------------------------
%  LaTeX2e Resume Template - Kamil K Wojcicki
%  @brief Josh Finnie's Resume stolen from Will Laurance
%----------------------------------------------------------------------------------------------------------------------
\documentclass[margin,line,10pt]{resume}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{multicol}

\raggedright

%----------------------------------------------------------------------------------------------------------------------
\begin{document}
\name{\Huge Josh Finnie \large Senior Software Developer}
\begin{resume}

%------------------------------------------------------------------------------------------------------------------
% Contact Information
%------------------------------------------------------------------------------------------------------------------
\section{\mysidestyle Contact\\Information\\\vspace{5pt}}

3900 14th St NW                     \hfill 860.716.5996\vspace{0mm}\\
Unit 402                            \hfill josh@jfin.us\vspace{0mm}\\
Washington, DC, USA 20011           \hfill \href{http://www.joshfinnie.com}{www.joshfinnie.com}\vspace{0mm}

%------------------------------------------------------------------------------------------------------------------
% Professional Experience
%------------------------------------------------------------------------------------------------------------------
\section{\mysidestyle Professional\\Experience\\\vspace{5pt}}

\textbf{Senior Software Maven}, \textsl{TrackMaven}\\March 2014 - Present\vspace{2mm}%
\begin{itemize}
    \item Works as a full stack software engineer for an all-in-one marketing analytics web application platform that pulls in data from customers' digital channels including social, earned \& owned media, traffic, and more.
    \item Developing testing protocols and best practices to support a full and successful transition of the live web application from CoffeeScript to ES2015. 
    \item Implementing a real-time tweet consumer platform collecting and analyzing over 2 million tweet a day. 
    \item Helped found and build a Quality and Infrastructure engineering team that focuses on promoting sound application infrastructure through ensuring high quality code and developing best practices across the engineering department.
\end{itemize}

\textbf{Software Developer IV}, \textsl{Koansys, LLC in support of DMI, Inc.}\\December 2012 - March 2014\vspace{2mm}%
\begin{itemize}
    \item Developed and deployed the \href{http://science.nasa.gov/iSat/}{Interactive Satellite Tracker (iSat)}, an application written in JavaScript that calculates satellite positioning in real-time based off of open-source data for Science@NASA, 
    \item Actively maintained iSat and created application enhancements to meet the needs of Science@NASA.
    \item Designed and built cloud infrastructure and automated scrips using Ansible to migrate Science@NASA’s Content Management System to Amazon Web Services.
    \item Transitioned Science@NASA’s Content Management System from Django to Drupal
\end{itemize}

\textbf{Front-end Developer}, \textsl{Koansys, LLC in support of Zerowait Corporation}\\December 2013 - March 2013\vspace{2mm}%
\begin{itemize}
    \item Designed a front-end  web application, using the Pyramid Framework and  written in Angular.js, which allows the customer to interact with a custom-built Python API.  
    \item Integrated the Zerowait application onto a FreeBSD box for customer testing.
\end{itemize}

\textbf{System Architect}, \textsl{Koansys, LLC in support of IndyPublish}\\August 2012 - October 2012\vspace{2mm}%
\begin{itemize}
    \item Rearchitected the existing web application to Amazon Web Services. 
    \item Rewrote customer web application from ASP.net and an Oracle database to Django and MySQL.
\end{itemize}

\textbf{Application Developer}, \textsl{Koansys, LLC in support of CROI, LLC}\\February 2012 - November 2013\vspace{2mm}%
\begin{itemize}
    \item Enhanced CROI’s web application by building a custom administration interface for customer user workload management.  
    \item Maintained up to date versions of the CROI application and MongoDB Data Base. 
    \item Transitioned CROI annual conference web application to Amazon Web Services  to support heightened traffic and database load. 
    \item Created scripting application to facilitate mass-mailing to CROI constituents.
\end{itemize}

\pagebreak

%------------------------------------------------------------------------------------------------------------------
% Skills
%------------------------------------------------------------------------------------------------------------------
\section{\mysidestyle Skills\\\vspace{5pt}}
\vspace{0mm}
\begin{multicols}{2}
    \textbf{Programming Languages: Frameworks}
    \begin{list2}
        \item Javascript: Node.js, Angular.js, React.js, jQuery
        \item Python: Django, Flask, Pyramid
        \item PHP: Wordpress, Drupal
        \item Other Languages: Go, Haskell, Clojure, Ruby
    \end{list2}
    \textbf{DevOPs}
    \begin{list2}
        \item Amazon Web Services (EC2, ELB, RDS, S3, Route53, IAM), Docker, Git/SVN, Ansible, Fabric
    \end{list2}
    \columnbreak
    \textbf{Databases}
    \begin{list2}
        \item PostgreSQL, Redis, MongoDB, MySQL, OracleDB
    \end{list2}
    \textbf{Web Programming \& Design}
    \begin{list2}
        \item HTML, CSS (Sass and Less), Jade, Bootstrap
    \end{list2}
    \textbf{Meetups}
    \begin{list2}
        \item Co-Organizer of NodeDC
        \item Co-Organizer of DockerDC
        \item Part-Time Co-Organizer of DCPython
    \end{list2}
\end{multicols}

%------------------------------------------------------------------------------------------------------------------
% Projects
%------------------------------------------------------------------------------------------------------------------
\section{\mysidestyle Highlighted Personal Projects\\\vspace{5pt}}
\textbf{BeerLedge}, \textsl{\href{https://www.beerledge.com}{https://www.beerledge.com}}\\
A web application that allows users to track and geotag beer selections.  Users can rate their selections on a 5 star
scale and create comments about their experience. The  application  is  built in Python and is self-hosted on Digital
Ocean.  The platform was originally developed using  the Flask micro-framework  and  MySQL.  Further development has
refactored the application to use Django 1.8 and PostgreSQL.

\textbf{PushFile}, \textsl{\href{https://www.npmjs.com/package/pushfile}{https://www.npmjs.com/package/pushfile}}\\
A command-line application written in Node.js which allows you to push a file to Amazon Web Services S3 and gives you
an URL in return. This is written in ES2015.

\textbf{React.js Tutorial}, \textsl{\href{http://www.joshfinnie.com/tag/reactjs/}{http://www.joshfinnie.com/tag/reactjs/}}\\
A series of blog posts walking people through the creation of a web application using React.js and Express.js. 

\textbf{How Old is this Metro Car}, \textsl{\href{http://www.howoldisthismetrocar.com}{http://www.howoldisthismetrocar.com}}\\
A web application that allows users to determine  the age of   Washington Metro Area Transit Authoritys’ traincars. The
application is  a single-page web application   built using Angular.js, written in JavaScript  and hosted exclusively on
Amazon Web Services  S3, a static service provider. 

%------------------------------------------------------------------------------------------------------------------
% Presentation
%------------------------------------------------------------------------------------------------------------------
\section{\mysidestyle Talks \& Presentations\\\vspace{5pt}}

\textbf{\href{http://www.joshfinnie.com/talks}{http://www.joshfinnie.com/talks}}\vspace{1mm}
\begin{list2}
    \item Dockerizing your Node App in 5 Minutes, \textsl{NodeDC}, March 17, 2016
    \item Command Line Applications in Node.js, \textsl{NationJS 2015}, November 13, 2015
    \item A DSL in Python, \textsl{Django District, etc.}, October 27, 2015
    \item A Pythonista's Day-O-Haskell, \textsl{TrackMaven Monthly Challenge}, September 30, 2015
    \item Sneaking React into Angular, \textsl{TrackMaven Monthly Challenge}, May 27, 2015
    \item iSat: Lightning Talk, \textsl{TrackMaven Monthly Challenge}, January 19, 2015
    \item Beer Search \& Recs in Elastic Search, \textsl{TrackMaven Monthly Challenge}, November 12, 2014
    \item Making BeerLedge Social, \textsl{Django District}, July 15, 2014
    \item NodeSchool Lightning Talk, \textsl{DC JQuery User Group}, June 02, 2014
    \item Building A Node.js Command Line Application, \textsl{NodeDC}, May 22, 2014
    \item Installing Drupal with Ansible, \textsl{DrupalDC}, February 10, 2014
\end{list2}

%------------------------------------------------------------------------------------------------------------------
% Education
%------------------------------------------------------------------------------------------------------------------
\section{\mysidestyle Education\\\vspace{5pt}}

\textbf{Certificates of Continuing Education}, \textsl{MongoDB University}\\
M101P: MongoDB for Developers, M102: MongoDB for DBAs\vspace{-3mm}

\textbf{Classes towards a Masters of Science}, \textsl{Central Connecticut State University}\\
Geography (Focus on Internet GIS)\vspace{-3mm}

\textbf{Bachelors of Art}, \textsl{University of Connecticut}\\
Economics (Certificate in Quantitative Economics \& Minor in Mathematics)\vspace{20mm}

\hfill Created in \LaTeX and last update on \today
%----------------------------------------------------------------------------------------------------------------------
\end{resume}
\end{document}

%----------------------------------------------------------------------------------------------------------------------
% EOF
%----------------------------------------------------------------------------------------------------------------------
